### 2009-03-24 doc/storage_system/arc-storage-documentation.tex
small update

\begin{verbatim}
    <Service name="pythonservice" id="bartender">
        <ClassName>storage.bartender.bartender.BartenderService</ClassName>
        <LibrarianURL>https://sal1.uppmax.uu.se:60000/Librarian</LibrarianURL>
        <ProxyStore>/var/arc/spool/proxy_store</ProxyStore>
        <GatewayClass>storage.bartender.gateway.gateway.Gateway</GatewayClass>
        <GatewayCfg>
            <ProxyStore>/var/arc/spool/proxy_store</ProxyStore>
            <CACertificatesDir>/etc/grid-security/certificates/
        </GatewayCfg>
        <ClientSSLConfig FromFile='clientsslconfig.xml'/>
    </Service>
\end{verbatim}

>>>>

\begin{verbatim}
    <Service name="pythonservice" id="bartender">
        <ClassName>storage.bartender.bartender.BartenderService</ClassName>
        <LibrarianURL>https://sal1.uppmax.uu.se:60000/Librarian</LibrarianURL>
        <ProxyStore>/var/arc/spool/proxy_store</ProxyStore>
        <GatewayClass>storage.bartender.gateway.gateway.Gateway</GatewayClass>
        <GatewayCfg>
            <ProxyStore>/var/arc/spool/proxy_store</ProxyStore>
            <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
        </GatewayCfg>
        <ClientSSLConfig FromFile='clientsslconfig.xml'/>
    </Service>
\end{verbatim}

### 2009-03-24 doc/storage_system/arc-storage-manual.tex
small update

>>>>

\section{Accessing external storage solutions} % (fold)
\label{sec:using_the_gateway}

install globus libraries

\begin{verbatim}
$ sudo mkdir /var/spool/arc/proxy_store
\end{verbatim}

\begin{verbatim}
<Service name="pythonservice" id="bartender">
    <ClassName>storage.bartender.bartender.BartenderService</ClassName>
    <LibrarianURL>https://storage:60000/Librarian</LibrarianURL>
    <ProxyStore>/var/spool/arc/proxy_store</ProxyStore>
    <GatewayClass>storage.bartender.gateway.gateway.Gateway</GatewayClass>
    <GatewayCfg>
        <ProxyStore>/var/spool/arc/proxy_store</ProxyStore>
        <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
    </GatewayCfg>
    <ClientSSLConfig FromFile="/etc/arc/clientsslconfig.xml" />
</Service>
\end{verbatim}
